Interpreting Random Forest Predictions for Firearm Identification Using LIME

### 2018-10-29 paper/paper.Rmd
worked on labelling bins

```{r setup, include = FALSE}
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, cache = TRUE)

@@

  # Apply the explain function from the lime package (with a seed set)
  set.seed(84902)
  hamby224_explain <- lime::explain(hamby224_test %>% select(rf_features), 
                                    hamby224_lime, 
                                    n_labels = 1, 
                                    n_features = 3)

@@

```{r echo = FALSE}
# Create the test_explain combined data if the file does not already exist
if(!file.exists("../data/hamby224_test_explain.rds")) {

@@

  # Reorder the variable of feature_desc for plotting purposes
  hamby224_test_explain <- hamby224_test_explain %>%
    mutate(
      feature_desc = reorder(feature_desc, strictly_less),
      feature_desc = reorder(feature_desc, feature_number),
      feature_desc = reorder(feature_desc, as.numeric(feature))
    )

>>>>

```{r setup, include = FALSE}
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, eval = TRUE)

@@

  # Apply the explain function from the lime package (with a seed set)
  set.seed(84902)
  hamby224_explain <- lime::explain(hamby224_test %>% select(rf_features), 
                                    hamby224_lime,
                                    labels = "TRUE",
                                    n_features = 3)

@@

```{r echo = FALSE}
# Function to use for creating bin labels in the test_explain dataset
bin_labeller <- function(bin_cuts, feature, feature_value){

  # Create a dataframe of bins cuts
  bin_cuts <- data.frame(matrix(unlist(hamby224_lime$bin_cuts), nrow = 9, byrow = TRUE)) %>%
    rename("Q0" = X1, "Q25" = X2, "Q50" = X3, "Q75" = X4, "Q100" = X5) %>%
    mutate(Feature = rf_features) %>%
    select(Feature, Q0:Q100)

  # Subset the bin cuts table to the selected feature
  feature_bin_cuts <- bin_cuts %>% filter(Feature == feature)

  # Determine which bin the case falls in
  if(feature_value < feature_bin_cuts$Q25){
    feature_bin <- "lower"
  } else if (feature_bin_cuts$Q25 <= feature_value & feature_value < feature_bin_cuts$Q50){
    feature_bin <- "lower middle"
  } else if (feature_bin_cuts$Q50 <= feature_value & feature_value < feature_bin_cuts$Q75){
    feature_bin <- "upper middle"
  } else if (feature_bin_cuts$Q75 <= feature_value){
    feature_bin <- "upper"
  }

  # Return the bin
  return(feature_bin)

```{r}
# Create the test_explain combined data if the file does not already exist
if(!file.exists("../data/hamby224_test_explain.rds")) {

@@

  # Reorder the variable of feature_desc for plotting purposes
  hamby224_test_explain <- hamby224_test_explain %>%
    mutate(feature_desc = reorder(feature_desc, strictly_less),
           feature_desc = reorder(feature_desc, feature_number),
           feature_desc = reorder(feature_desc, as.numeric(feature))) %>%
    mutate(feature_bin = mapply(bin_labeller, feature = feature, feature_value = feature_value)) %>%
    select(case:feature_desc, feature_number:feature_bin, data, prediction)
